On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update Methods introduction

\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x})_j$ can be represented (possibly inaccurately) as a sum over $K$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:

@@

  f({\vec{x}})_j \; = \; \sum_{k=0}^{K} \; \mu_{k} \, \phi_{kj}\; .

@@

In particular, defining $\hat{U} = \{\phi_{kj}\}$, and $\vec{f} = \{f_j\}$, then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that

@@

To consider these two approaches in a largely automated way (i.e. where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.

>>>>

\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x}_j)$ can be represented (possibly inaccurately) as a sum over $K$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:

@@

  f({\vec{x}}_j) \; = \; \sum_{k=0}^{K} \; \mu_{k} \, \phi_k(\vec{x}_j)\; .

@@

In particular, defining ${U}_{jk} = \phi_k(\vec{x}_j)$, $f_j = f(\vec{x}_j)$ then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that

@@

To consider these two approaches in a largely automated way (i.e. where the set of possible basis functions is known, but the selected basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
